%!TEX root = thesis.tex

\section{Genus One Moduli Space}
% \epigraph{All analytic functions are alike; each non-analytic function is non-analytic in its own way.}

\subsection{Intro}
\label{sub:Intro}

An outline:
\begin{enumerate}
\item
Give the outline
\item
Compute a basis of differentials with the correct symmetries
\item
Compute their periods and a basis of differentials
\item
Introduce the various moduli spaces we will consider
\item
Formulate the conditions
\item
Reformulate in coordindates more suited to calculation.
\item
Talk about shape of this parameter space.
\item
Talk about $T$ and its multi-defined-ness. Universal cover
\item
Uniform coordinate
\item
Show derivative is nonzero
\item
Apply Implicit Function theorem in uniform coord and k
\item
Go to the Winchester, have a pint, and wait for this to blow over.
\end{enumerate}

The different moduli spaces we could be interested in

There are several interrelated moduli spaces of spectral data that we could be interested in. Spectral data is a triple $(Σ,Θ,\tilde{Θ})$ of a spectral curve $Σ$ and a pair of differentials on it. We know that every spectral curve has many differentials with with correct poles and symmetries. Spectral curves are parameterised by their branch points, and by symmetries we need only track branch points inside the unit circle. By counting degrees, we know there is a plane of such differentials with purely imaginary periods, but in general not every spectral curve will satisfy the further condition that there is a rank two lattice of differentials within this plane that have integral periods. Let the space of spectral curves that have \emph{integral} differentials be denoted $\mathcal{A}$. Within this space we could impose the further condition, the closing condition, on the differentials that requires their integrals over the marked points to also be integral. We shall call such differentials \emph{closing}, and the space of spectral curves with closing differentials $\mathcal{A}'$.

One can note that the plane of differentials with imaginary periods is naturally thought of as a rank two vector bundle over the space of spectral curves. Thus the moduli of spectral data can be thought of as bundles over $\mathcal{A}$ or $\mathcal{A'}$, depending on exactly whihc conditions one is imposing. Our ultimate aim will be to describe $\mathcal{M}$, the moduli of closing differentials, which is a rank two lattice bundle over $\mathcal{A'}$.

If we are considering only spectral curves of a fixed genus, we will use a subscript on the moduli space to denote this.

In the genus one case, every spectral curve admits integral differentials but not every one admits closing differentials. The closing conditions therefore can be viewed as defining equations for $\mathcal{A'}_1$ within $\mathcal{A}_1 = D^2 \setminus \{α=β\}$. We will investigate the topology of this space and show it to be simply connected. In doing so we will develop an explicit parameterisation of this space. The moduli space $\mathcal{M}_1$ will therefore be the trivial bundle.

In the calculations that follow, we will actually work with a cover of the space of spectral curves. A spectral curve is determined by its branch points, but we will consider instead ordered pairs of branch points. This introduces no complications in the genus one case, as both spaces are smooth and the ordered version is a degree two cover of the unordered version.








\subsection{Differentials of the Elliptic Spectral Curve}
One can deduce by abstract arguments that in the case of an elliptic spectral curve that the space of differentials is spanned by an exact differential and one with a period of $2π\iu$. The former can be written easily, but to find the latter it is necessary to compute the periods of certain forms. Consider the elliptic curve
\[
η^2 = P(ζ) = (ζ-α)(1-\bar{α}ζ)(ζ-β)(1-\bar{β}ζ)
\]
and the Legendre standard form
\[
w^2 = (1-z^2)(1-k^2z^2)
\]
where $k$ is the elliptic modulus. We desire to know the (Mobi\"us) transformation between these two curves. First, what are the permitted values of $k$? Consider the cross ratio
\[
\frac{\abs{α-β}^2}{\abs{1-\bar{α}β}^2} = [α,\cji{α};β,\cji{β}]
= [1,-1;k^{-1},-k^{-1}] = \bra{\frac{k-1}{k+1}}^2.
\]
Choosing signs so that $0<k<1$, we arrive at
\[
k = \frac{\abs{1-\bar{α}β}-\abs{α-β}}{\abs{1-\bar{α}β}+\abs{α-β}}.
\]
Because of the reality structure of the spectral curve, $k$ is forced to be real. The two extreme cases of $k=0$ and $k=1$ occur exactly when of pair of branch points collasce on the unit circle and when $α=β$ respectively, the two ways this curve can degenerate to a singular curve. With the modulus fixed, the formula for the transformation can be found by rearranging the relation $[ζ,β;α,\cji{α}] = [f(ζ),k^{-1};1,-1]$ to get
\begin{align}
A &:= (α-β)\abs{1-\bar{α}β} \\
B &:= (1-\bar{α}β)\abs{α-β} \\
z = f(ζ) &= \frac{ζ(\bar{α}A + B) - (A + αB)}{ζ(\bar{α}A - B) - (A - αB)} \\
ζ = f^{-1}(z) &= \frac{-z(A-αB) + (A+αB)}{-z(\bar{α}A-B) + (\bar{α}A+B)} \\
den &:= ζ(\bar{α}A-B) - (A - αB)\\
ned &:= -z(\bar{α}A-B) + (\bar{α}A+B)
\end{align}
Because of the holomorphic involution $η\to-η$, this formula almost but not quite specifies a relation between $η$ and $w$. There is a free sign choice to make. In $(ζ,η)$ there is a notion of the `upper' unit circle, the one on which $η$ is positive over $ζ=1$. More generally, on this copy of the unit circle in $Σ$, $η(ζ)=ζ\abs{ζ-α}\abs{ζ-β}$. Under the transformation the unit circle is mapped to the imaginary axis. On the imaginary axis, $w(iσ) = \pm \sqrt{1+σ^2}\sqrt{1+k^2σ^2}$ so also has a notion of an upper sheet. The sign choice needed to make the upper unit circle map to the upper imaginary axis is
\[
η = \frac{AB\bra{1-\abs{α}^2}\bra{\abs{α-β}+ \abs{1-\bar{α}β}}}{ned^2}w
\]
There is another aspect of the projective geometry of the transformation that bears mention. The four points $α,\cji{α},β,\cji{β}$ are mapped to $1,-1,k^{-1},-k^{-1}\in\R$. Therefore the four points themselves are concyclic (or lie on a line). The intersection of this circle (which we will refer to as the branch point circle) with the unit circle correspond to the points $z=0$ and $z=\infty$, which are the intersections of the real and imaginary axes. $z=0$ lies between $α$ and $\cji{α}$ and similiarly $z=\infty$ lies between $β$ and $\cji{β}$.

From here we perform a sequence of computations. Firstly, how do the holomorphic differential of each coordinate compare (ie what is the scaling factor)? And what about the standard differential of the second kind?
\begin{align}
\tilde{ω} &:= \frac{dz}{w} \\
ω := \frac{dζ}{η} &= \frac{-2}{\abs{α-β} + \abs{1-\bar{α}β}}\tilde{ω} \\
e := (1-k^2z^2)\frac{dz}{w} &= \frac{-2AB(1-\abs{α}^2)^2}{\abs{α-β} + \abs{1-\bar{α}β}}\cdot\frac{(ζ-β)(1-\bar{β}ζ)}{den^2}\frac{dζ}{η}
\end{align}
We construct the desired differentials in two stages. First, we narrow the space to a 3 dimensional one, and then compute the periods of its basis. This then allows us to find the differentials inside that space with the correct periods. The holomorphic differential is real (in the sense that $ρ^*ω = -\bar{ω}$), is it make an obvious first basis vector. In genus one, there is also an exact differential with the correct pole behaviour, namely
\[
Θ_1^1 := d\left( \iu\frac{η}{ζ} \right)
= \iu\left[ -αβ + \frac{1}{2}\left(α(1+\abs{β}^2) + β(1+\abs{α}^2)\right)ζ - \frac{1}{2}\left(\bar{α}(1+\abs{β}^2) + β(1+\abs{α}^2)\right)ζ^3 + \bar{α}\bar{β}ζ^4 \right]\frac{dζ}{ζ^2η}
\]
The restriction that the differentials have double poles at $ζ=0,\infty$ means that the polynomial part must be degree four. The restiction that these poles have no residues means that the bottom and top terms determine the linear and third order terms. And finally the reality condition means that the middle term must be real and the top term is the conjugate of the bottom term. In effect, we only have a complex number of choice in the bottom term and a real scalar in the middle term. Given the two differentials we have already choosen, an obvious way to complete the basis would be to take
\[
λ = \left[ -αβ + \frac{1}{2}\left(α(1+\abs{β}^2) + β(1+\abs{α}^2)\right)ζ + \frac{1}{2}\left(\bar{α}(1+\abs{β}^2) + β(1+\abs{α}^2)\right)ζ^3 - \bar{α}\bar{β}ζ^4 \right]\frac{dζ}{ζ^2η}
\]
This is a differential of the second kind, so we can express it as the sum of the standard differential of the second kind $e$ exact differentials of the second kind and the holomorphic differential. We assemble several pieces. In the $(z,w)$ plane, the pole of $e$ is at infinity. Let $x=z^{-1}$ and expand in this coordinate
\begin{align*}
dz &= - x^{-2}dx \\
w &\sim x^{-2} \bra{k - \frac{1}{k}\frac{1+k^2}{2}x^2 + \dots} \\
e &\sim (-1+k^2x^{-2}) \frac{x^{-2}dx}{x^{-2}} \bra{k + \frac{1}{k}\frac{1+k^2}{2}x^2 + \dots} \\
&= dx \bra{k^3x^{-2} + \bra{\frac{1}{k}\frac{1+k^2}{2}-k}x^0 + \dots}
\end{align*}
which shows that $e$ has a double pole with no residue. In the $ζ$-plane, this pole is not at either zero or infinity, so we add an exact differential to cancel this misplaced pole.
\[
e - Nd\left(\frac{η}{den}\right) := e + \frac {2(\bar{α}A-B)} {\abs{α-β}+\abs{1-\bar{α}β}} d\left(\frac{η}{den}\right)
\]
is holomorphic on $\C$, since with $N$ chosen match the strength of the double pole, and because they are both residue free, the two poles must cancel completely. Likewise, so too is
\[
λ - d\left(\frac{η}{ζ}\right) = \left[ \left(\bar{α}(1+\abs{β}^2)+β(1+\abs{α}^2)\right)ζ^3 - 2\bar{α}\bar{β}ζ^4 \right]\frac{dζ}{ζ^2η}
\]
holomorphic on $\C$. Hence all the poles have been moved to infinity. We choose a scaling to cancel these as well.
\begin{align}
λ - d\left(\frac{η}{ζ}\right) &\sim M \left( e - Nd\left(\frac{η}{den}\right) \right) \\
\implies M &= -\bra{\abs{α-β}+\abs{1-\bar{α}β}}
\end{align}
So the difference of the two sides above is holomorphic on the whole spectral curve, a compact Riemann surface of genus one, and therefore a multiple of $ω$.
\[
Lω := λ - d\left(\frac{η}{ζ}\right) - M \left( e - Nd\left(\frac{η}{den}\right) \right)
\]
Evaluating both sides at $ζ=0$ yields
\[
(αB-A)^2L = 2βAB(1-\abs{α}^2)^2 + (\bar{α}A-B)(αB-A)P'(0) - 2αβ(\bar{α}A-B)^2
\]
At this point, we have computed the coefficents $L,M,N$ and can write
\[
    λ = Lω + Me + exact
\]
which is sufficent to be able to compute its periods in terms of the standard elliptic integrals. In the $ζ$-plane, let $γ_R, γ_I$ denote the real and imaginary periods respectively. We will choose the basis in the following way. For $γ_R$, start on the upper unit circle, traverse in and around $α$ anticlockwise, then cross the lower unit circle and continue anticlockwise around $\cji{α}$ before returning to the starting point. For $γ_I$, start at the same point we began $γ_R$ and follow the unit circle anticlockwise. The image of $γ_R$ under $f$ is the anticlockwise loop around $-1$ and $1$ with the left to right part of the path on the upper sheet. $f(γ_I)$ is simply a traversal of the imaginary axis from top to bottom on the upper sheet. But this is homologous to the standard anticlockwise loop around $1$ and $k^{-1}$. To summarise the standard elliptic integrals
\begin{align}
\int_{f(γ_R)}\tilde{ω} &= 4K(k) \\
\int_{f(γ_I)}\tilde{ω} &= 2\iu K' \\
\int_{f(γ_R)}e &= 4E(k) \\
\int_{f(γ_I)}e &= 2\iu(K'-E')
\end{align}
where $K$ and $E$ are the complete elliptic integrals of the first and second kind, and the prime denote not the derivative but instead the complement. By definition $k' = \sqrt{1-k^2}$ and $K'(k) = K(k')$ and ditto for $E'$. The periods for our basis are
\begin{align}
\int_{γ_R} λ &= 8\frac{L}{M}K + 4 ME \\
\int_{γ_I} λ &= 2\iu(2\frac{L}{M}+M)K' - 2\iu M E'
\end{align}
Let $Θ_1^2 = Ωω + Λλ$ and we wish for this differential to have a real period of zero and an imaginary period of $2π\iu$. That requires
\begin{align}
K(\frac{2}{M}Ω + \frac{2}{M}LΛ) + MΛE &= 0 \\
K'(\frac{2}{M}Ω + \frac{2}{M}LΛ + MΛ) -MΛE' &= \pi
\end{align}
From the first equation, we can write $ MΛ = - ΓK$ and the multiple of the $K$ as $ΓE$. Substituting this into the second equation gives
\begin{align}
\pi
&= K'(ΓE - ΓK) + ΓKE' \\
&= Γ(K'E + KE' - KK') \label{eq:legendre_relation}\\
&= \frac{\pi}{2}Γ \\
Γ &= 2 \\
Λ &= -\frac{2}{M}K \\
Ω &= 2\frac{L}{M}K + ME
\end{align}
where \eqref{eq:legendre_relation} uses Legendre's relation. We can unwind these definitions a little to yield
\begin{align}
Θ_1^2
&= ME ω - 2Ke - \frac{2}{M}K\left[ d\bra{\frac{η}{ζ}} - MNd\bra{\frac{η}{den}} \right]\\
&= 2E \tilde{ω} - 2Ke - \frac{2}{M}K\left[ d\bra{\frac{η}{ζ}} - MNd\bra{\frac{η}{den}} \right]
\end{align}
which shows a nice division, with the first two terms providing the desired periods and the last two terms giving the required pole behaviour. One could also arrange things as follows
\[
Θ_1^2 = 2E \tilde{ω} - 2K\bra{e - Nd\bra{\frac{η}{den}}} - \frac{2}{M}K d\bra{\frac{η}{ζ}}
\]
so that each term is holomorphic on at least $ζ\in\C^*$. With this differential found, every differential that meets the conditions is of the form $a Θ_1^1 + n Θ_1^2$ for some $a\in\R$ and $n\in\Z$.









\subsection{The Closing Conditions}
Recall the closing conditions. These are the conditions that spectral data must meet in order that they correspond to a harmonic map from the torus, rather than a harmonic map of the plane (of finite type). If $(Σ,Θ,\tilde{Θ})$ is a triple of spectral data, $Θ$ satisfies the closing condition at $ζ=1$ if
\[
\int_{γ_{+}} Θ \in 2π\iu \Z,
\]
where $γ_+$ is a path that begins at $(1,η(1)^-)$ and ends at $(1,η(1)^+)$, the two points on the spectral curve lying over $ζ=1$. However, the value of the integral is dependent on the particular path chosen. To see that this condition is well defined, suppose that $γ$ and $γ'$ are two paths between the two points over $ζ=1$. Their difference $γ-γ'$ is a closed loop and homologous to an integral combination of periods $aγ_R + bγ_I$. The difference in the values of the integrals is therefore
\[
\int_{γ} Θ - \int_{γ'} Θ
= \int_{γ - γ'} Θ
= a\int_{γ_R} Θ + b\int_{γ_I} Θ
= 2π\iu nb,
\]
because by the period conditions, the real period of $Θ$ is zero and its imaginary period is a multiple of $2π\iu$. So although the value of the integral is dependent on the path, the condition that the value must lie in $π\iu \Z$ is not. Likewise, the closing condition at $ζ=-1$ is defined by taking $γ_-$, a path from $(-1,η(-1)^-)$ to $(-1,η(-1)^+)$, and requiring the integral of $Θ$ over this path to lie in $2π\iu \Z$ also.

For an exact differential, the particular path of integration is irrelevant and the value of the integral is well defined.
\[
\int_{γ_{+}}Θ_1^1 = i \left. d\bra{\frac{η}{ζ}} \right|_{(1, η(1)^-)}^{(1, η(1)^+)} = 2i η(1)^+ = 2i \abs{1-α}\abs{1-β}
\]
And similiarly for the other path
\[
\int_{γ_{-}} Θ_1^1 = 2i η(-1)^+ = -2i \abs{1+α}\abs{1+β}.
\]
One can use these formulae to define an explicit condition for a spectral curve to admit an exact closing differential. An exact closing differential must be a real multiple of $Θ^1$. Let the scaling factor be $a$. The two closing conditions applied to $a Θ^1$ are then
\begin{align*}
2\iu η(1)^+ a &\in 2π\iu \Z, \\
-2\iu η(-1)^- a &\in 2π\iu \Z.
\end{align*}
Eliminating $a$ from the two equations, there is a common solution for $a$ if and only if
\[
p := \frac{η(1)^+}{-η(-1)^-} = \frac{\abs{1-α}\abs{1-β}}{\abs{1+α}\abs{1+β}} \in \Q^+.
\]
In other words, if and only if $p(α,β)$ is a positive rational. This gives the flavour of what we are aiming to achieve. We would like to give conditions on a spectral curve that ensures it admits closing spectral data, and we would like to give such conditions explicitly so we can give results on the subspace of such spectral curves within the space of all spectral curves.

Before we plow ahead to differentials with periods, there is a simplification we can make. Suppose that a spectral curve admits a pair of closing differentials $Θ,\tilde{Θ}$ with periods $2π\iu n, 2π\iu \tilde{n}$ respectively. Let $g$ be the greatest common denominator of $n$ and $\tilde{n}$ (choosen to be a positive number), and by Bezout's identity let $x,y$ be the integers that satisfy
\[
xn + y\tilde{n} = g.
\]
Then consider the differentials $Ψ,\tilde{Ψ}$ defined by the following integer combination
\[
\vt{Ψ}{\tilde{Ψ}} =
\begin{pmatrix}
\tfrac{\tilde{n}}{g}    &   -\tfrac{\tilde{n}}{g} \\
x                       &   y
\end{pmatrix}
\vt{Θ}{\tilde{Θ}}
\]
The new pair of differentials are simpler in the sense that their periods are $0$ and $2π\iu g$ respectively. They are also closing, because they are an integer combination of closing differentials. And the integer matrix has determinant one, so is invertible over the integers. Further, the two differentials are linearly dependent exactly when $Ψ$ is zero. Hence a curve admits linearly independent closing differentials if and only if it admits nonzero closing differentials with periods $0$ and $2π\iu g$, for some positive integer $g$.

Thus the condition above, $p\in\Q^+$, is one conditon a spectral curve must satify. To find the other condition, concerning the differential with period $2π\iu g$, we follow the same line of reasoning. For some real number $b$, we may write $\tilde{Ψ} = b Θ^1 + g Θ^2$. The two closing conditions applied to this are then
\begin{align*}
2η(1)^+ \iu b + g\int_{γ_+} Θ^2 &= 2π\iu Γ^+ \in 2π\iu \Z, \\
-2η(-1)^+ \iu b + g\int_{γ_-} Θ^2 &= 2π\iu Γ^- \in 2π\iu \Z.
\end{align*}
Again, elimination of $b$ yields the condition for a common solution to exist. This equation can be written as
\[
2π\iu T := p \int_{γ_-} Θ^2 - \int_{γ_+} Θ^2 = 2π \iu \frac{p Γ^- - Γ^+}{g}.
\]
The right hand side is made up of constants, and may take any value that is an integer multiple of $2π\iu / g\,\text{denom}(p)$.

\begin{lem}
A spectral curve admits a pair of nonzero closing differentials, one exact and one inexact, if and only if $p\in\Q^+$ and $T\in\Q$.

\begin{proof}
From the above, this is a necessary condition.

For the converse suppose that the are both rational, say $p = n/m$ and $T = n'/m'$ in lowest terms. Then we may write
\[
T = \frac{n'}{m'} = \frac{n'm}{m'm} = \frac{n Γ^- - mΓ^+}{gm}.
\]
And so we can see that we should take $g$ to be $m'$. Let $x,y$ be integers such that $xm-ny = 1$. Then we may take
\[
Γ^+ = n'mx,\;\; Γ^- = n'my,
\]
to obtain equality of the numerator. Hence the condition for the existence of a consistent solution for $b$ is met. The rationality of $p$ ensures the existence of an $a$. Having found $a,b$ and $g$ such that $Ψ = aΘ^1, \tilde{Ψ} = bΘ^1 + gΘ^2$ solve the closing conditions, we have demonstrated that the spectral curve admits closing differentials.
\end{proof}
\end{lem}

Thus the space $\mathcal{A'}_1$, the space of genus one spectral curves that admit closing spectral data is defined by the equations $p(α,β) \in \Q^+, T(α,β) \in \Q$. In general the closing conditions are difficult to work with, harder than even the period conditions. In the genus one case that we are dealing with for example, $Θ_1^1$ leads to an algebraic expression but $Θ_1^2$ leads to a transcendental conditions involving incomplete elliptic integrals.

To close this section, we shall write out a formula for $T$. The essential computation is that of the integral of $Θ^2$ over the paths $γ_+,γ_-$, but the value of the integral is dependent on the particular paths chosen. Let us then make a principal choice of paths, and let the value of $T$ on these principal choices be denoted $T_0$. Let $γ_+$ be the path that begins at $(1,-η(1))$, traverses the unit circle to the point $μ$ without crossing $ν$, follows the branch point circle to $α$, circles this branch point anticlockwise, goes back along the arc (though on a different branch now) to the unit circle, and back to $(1,+η(1))$. Likewise for $γ_-$ from $(-1,-η(-1))$ to $(-1,η(-1))$. This choice is not globally well defined; when $ν=\pm 1$ it is impossible to `avoid' $ν$. For the moment, suppose this is not the case.

In $(z,w)$ coordinates these paths are easy to describe (deliberately so). Start from the point $f(1)$ on the imaginary axis, go to the origin and out along the real axis, around $z=1$ (which corresponds to $ζ=α$) and back again. By taking the path that avoids $ν$, which corresponds to $z=\infty$, we keep to the realm of path integrals in the plane. We can derive explicit formula for the value of the integrals on these particular paths.
\begin{align}
\int_{γ_+} \tilde {ω}
&= \bra{2\int_0^{f(1)} - 2\int_0^1} \tilde {ω} \\
&= 2 F(f(1);k) - 2 K(k) \\
\int_{γ_+} e
&= 2 \tilde E(f(1);k) - 2 E(k) \\
\int_{γ_+} Θ_1^2
&= \int_{γ_+} (2E \tilde{ω} - 2Ke) - \frac{2}{M}K \int_{γ_+} \left[ d\bra{\frac{η}{ζ}} - MNd\bra{\frac{η}{den}} \right] \\
&= 4E F(f(1)) - 4K E(f(1)) - \frac{4K}{M} η(1)^+\left[ 1 - \frac{MN}{den(1)} \right] \\
&= 4 E(k) \tilde{F}(f(1);k) - 4 K(k) \tilde{E}(f(1);k) - 4K(k) \frac{\abs{1-α}\abs{1-β}}{\abs{α-β} + \abs{1-\conj{α}β}} \frac{1+ν}{1-ν}.
\end{align}

For the closing condition at $ζ=-1$
\begin{align}
\int_{γ_-} Θ_1^2
&= 4EF(f(-1)) - 4K\tilde{E}(f(-1)) - \frac{4K}{M} η(-1)^+\left[ 1 - \frac{MN}{den(-1)} \right] \\
&= 4 E(k) \tilde{F}(f(-1);k) - 4 K(k) \tilde{E}(f(-1);k) - 4K(k) \frac{\abs{1+α}\abs{1+β}}{\abs{α-β} + \abs{1-\conj{α}β}} \frac{1-ν}{1+ν}.
\end{align}

From these we explictly compute
\begin{align*}
2π\iu T_0 &=  p \int_{γ_-} Θ^2 - \int_{γ_+} Θ^2 \\
&=  p \left[ 4 E \tilde{F}(f(-1)) - 4 K \tilde{E}(f(-1)) - 4K \frac{\abs{1+α}\abs{1+β}}{\abs{α-β} + \abs{1-\conj{α}β}} \frac{1-ν}{1+ν} \right] \\
&\qquad\qquad   - \left[ 4 E \tilde{F}(f(1)) - 4 K \tilde{E}(f(1)) - 4K \frac{\abs{1-α}\abs{1-β}}{\abs{α-β} + \abs{1-\conj{α}β}} \frac{1+ν}{1-ν} \right] \\
&=  4p \left[ E \tilde{F}(f(-1)) - K \tilde{E}(f(-1)) \right] - 4\left[ E \tilde{F}(f(1)) - K \tilde{E}(f(1)) \right] \\
&\qquad\qquad    - 4K\left[ p\frac{\abs{1+α}\abs{1+β}}{\abs{α-β} + \abs{1-\conj{α}β}} \frac{1-ν}{1+ν} - \frac{\abs{1-α}\abs{1-β}}{\abs{α-β} + \abs{1-\conj{α}β}} \frac{1+ν}{1-ν} \right]  \\
&=  4p \left[ E \tilde{F}(f(-1)) - K \tilde{E}(f(-1)) \right] - 4\left[ E \tilde{F}(f(1)) - K \tilde{E}(f(1)) \right] \\
&\qquad\qquad    - 4K \frac{\abs{1-α}\abs{1-β}}{\abs{α-β} + \abs{1-\conj{α}β}} \left[ \frac{1-ν}{1+ν} - \frac{1+ν}{1-ν} \right]  \\
&=  4p \left[ E \tilde{F}(f(-1)) - K \tilde{E}(f(-1)) \right] - 4\left[ E \tilde{F}(f(1)) - K \tilde{E}(f(1)) \right] + 4K \frac{\abs{1-α}\abs{1-β}}{\abs{α-β} + \abs{1-\conj{α}β}} \frac{4ν}{1-ν^2}. \labelthis{Teqn} \\
\end{align*}

Previously, the comment was made that the particular algorithm to chose a path is not valid when $ν = \pm 1$. Indeed, the result of this can be seen directly in the formula we have derived for $T_0$, which is not defined when $ν$ take either of these values. Properly understood, $T$ is not a function on the space of genus one spectral curves $\mathcal{A}_1$, but rather it is a function on the space of paths $(γ_+, γ_-)$, which we shall call $\mathcal{P}$. To be more precise, let $\mathcal{P}$ be the space $\{(γ_+, γ_-, α)\}$ where $α$ is one of the branch points inside the unit circle of some genus one spectral curve $Σ$ and $γ_+$ and $γ_-$ are paths $(0,1) \to Σ$ defined in the following way. $γ_+$ starts at $(1, η(1)^-)$, tranverses the unit circle to $μ$ (in any manner one pleases), goes along the branch point circle to $α$, encircles it, returns to $μ$ along the branch point circle and retraces its path to $(1, η(1)^+)$. In an analogous way, $γ_-$ starts at $(-1, η(-1)^-)$ and finishes at $(-1, η(-1)^+)$. We consider these paths up to homology.

\todo{worry} It is possible that since this is not the full space of paths, there are spectral curves that admit closing differentials, but the fact they are closing can only be seen on certain paths that are excluded here. I don't think that is the case, because every path is homologous to one of these up to the addition of some number of periods, which do not change the closing condition. On the other hand, the reason that it is not sufficent to consider the principal paths is that they are not defined on every spectral curve.

$\mathcal{P}$ is naturally a $\Z^2$-bundle over the space of spectral curves with a distinguished branch point. The projection map takes a triple $(γ_+, γ_-, α)$ to the underlying spectral curve $Σ$. The fibre over any spectral curve $Σ$ is seen to be $\Z^2$, because if one fixes a point on the upper unit circle, not lying over $1,-1,μ$, the (signed) number of crossings of that point by a path uniquely determines that path. As an aside, the issue with points over $1,-1$ and $μ$ is that the paths may terminate there (in the obvious way for the first two, in the sense that the path may leave the unit circle in the latter case). One could probably introduce a convention to get around this, but it is not necessary to do so for our purposes.

Viewed from this perspective, we consider $T$ to be a multivalued function on $\mathcal{A}_1$ defined locally up the addition of multiples of $p$ and $1$, and $T_0$ is a principal branch cut. We call $\tilde{T}$ the well defined version that is defined on $\mathcal{P}$. $\mathcal{P}$ is actually a cover of the universal cover of $\mathcal{A}_1$ (implying it is disconnected), a fact that will become apparent once we have adopted coordinates on $\mathcal{A}_1$ better adapted to the situation.







\subsection{Marked Point Coordinates}
\label{sub:Reformulate}

Recall the two rationality conditions that must be satisfied for a genus one spectral curve to admit differentials meeting the closing condition
\begin{align}
p &:= \frac{\abs{1-α}\abs{1-β}}{\abs{1+α}\abs{1+β}} \in \Q^+, \\
T &:=  \frac{1}{2π\iu} \bra{p\int_{γ_-} Θ^2 - \int_{γ_+} Θ^2} \in \Q,
\end{align}
Using the formula for the differentials, we can explicitly give an expression for the principal branch of $T$ in terms of the branch points $α$ and $β$
\[
T_0 = \frac{2p}{π\iu} \left[ E F(f(-1);k) - K E(f(-1);k) \right] - \frac{2}{π \iu}\left[ E F(f(1);k) - K E(f(1);k) \right] + \frac{2}{π\iu}K \frac{\abs{1-α}\abs{1-β}}{\abs{α-β} + \abs{1-\conj{α}β}} \frac{4ν}{1-ν^2}, \labelthis{Teqn1}
\]
where $f$ is the map normalises the branch points of the spectral curve (it takes $α$ to $1$, $β$ to $k$, etc) and $ν$ is the point of intersection between the branch point circle and the unit circle. $T$ is a real valued function because $f(1)$ and $f(-1)$ are purely imaginary and $F, E$ take the imaginary axis to itself, and because $ν$ is on the unit circle, $ν/(1-ν^2)$ is purely imaginary as well.

It is our ultimate aim to examine the surfaces defined by the two conditions and our examination will result in coordinates for those surfaces. This involves applying the implicit function theorem and the necessary computation for that theorem requires differentiating the above expressions. It is therefore prudent to adopt a parameterisation of the space of spectral curves more suited to that task than $(α,β)$. An obvious first coordinate is $p$ itself, as then we can enforce the first condition simply by holding it constant. Elliptic integrals are the most difficult part of the above to differentiate, so to minimise our labour we choose the other three (real) coordinates to be $k$, $\iu u = f(1)$ and $\iu v = f(-1)$.

This motivation misses some of the subtleties of the situation however. For example, $f$ is a M\"obius transformation of $\CP^1$, so may take the value infinity. We therefore make the following definition.

\begin{defn}\label{defn:parameter space}
Consider the product space $\R_{>0} \times (0,1) \times \RP^1 \times \RP^1$. Let $p \in \R_{>0}$ and $k \in (0,1)$ be coordinates on the first two factors. Let $u, u' \in \R$, with $u' = u^{-1}$, be coordinates covering the third factor, and likewise let $v, v' \in\R$, with $v' = v^{-1}$ be coordinates covering the fourth factor. Together, the four coordinate patches $(p,k,u,v)$, $(p,k,u',v)$, $(p,k,u,v')$ and $(p,k,u',v')$ to $\R_{>0} \times (0,1) \times \R^2$ cover $\R_{>0} \times (0,1) \times \RP^1 \times \RP^1$.

Consider the hypersurface $H$ that is the closure of $\{u=v\}$. In each of the four coordinate patches it is given by the equations $u=v$, $(u')^{-1} = v$, $u = (v')^{-1}$, $u' = v'$. Define $P$ to be the complement of $H$.
\end{defn}

First we must show that $P$ does indeed parameterise the space of spectral curves. We proceed by determining a formula for the change of parameters from $(α,β)$ to $(p,k,u,v)$. The forward direction has already been achived. The map $f$ is written in terms of $(α,β)$ \todo{ref} and the new parameters are the images of points under this map (except for $p$, which has its own formula in terms of $α$ and $β$). As the new parameters all respresent points in the $z$-plane, one method to derive the reverse change in parameters is to express the inverse transformation $f^{-1}(z)$ in term of our new parameters. Then $α = f^{-1}(1)$ and $β = f^{-1}(k^{-1})$, entirely analogous to to forward direction. Denote $z_0 = f(0)$, the image of $ζ=0$ in the $z$-plane. The real structure of the $z$-plane then forces $f(\infty) = - \conj{z_0}$. As a M\"obius transformation is described up to a scalar by the points sent to $0$ and $\infty$, $f^{-1}$ is a scalar multiple of
\[
\frac{z-z_0}{z + \conj{z_0}},
\]

Note the following trick using cross ratios.
\[
\abs{\frac{α-1}{α+1}}
= \abs{\frac{α-1}{α+1}} \abs{\frac{0+1}{0-1}}
= \abs{ \cross{α}{0}{1}{-1} }
= \abs{ \cross{1}{z_0}{\iu u}{\iu v} }
= \abs{\frac{1-\iu u}{1 - \iu v}} \abs{\frac{z_0 - \iu v}{z_0 - \iu u}}
\]
The same trick gives a similar formula for $β$.
\[
\abs{\frac{α-1}{α+1}}
= \abs{\frac{1-k\iu u}{1 - k\iu v}} \abs{\frac{z_0 - \iu v}{z_0 - \iu u}}
\]
The terms on the left are the two halves of the expression for $p$. Multiplying and expanding shows that for fixed values of the parameters $(p,k,u,v)$, $z_0$ lies on a particular circle. Let $z_0 = x+\iu y$.
\begin{align*}
p &= \abs{\frac{1-\iu u}{1 - \iu v}}\abs{\frac{1 - k\iu u}{1 - k\iu v}} \abs{\frac{z_0 - \iu v}{z_0 - \iu u}}^2 \\
\abs{\frac{z_0 - \iu v}{z_0 - \iu u}} ^2
&= p \frac{\sqrt{1+v^2}}{\sqrt{1+u^2}}\frac{\sqrt{1+k^2v^2}}{\sqrt{1+k^2u^2}} \\
&= p \frac{w(v)}{w(u)} \\
\abs{z_0 - \iu v} ^2 &= p \frac{w(v)}{w(u)} \abs{z_0 - \iu u}^2 \\
x^2 + y^2 &+ 2y \frac{puw(v) - vw(u)}{w(u)-pw(v)} + \frac{v^2w(u) - pu^2w(v)}{w(u)-pw(v)} = 0.
\end{align*}

In the $ζ$-plane, the points $-1,0,1$ all lie on a straight line that is perpendicular to the unit circle at both $-1$ and $1$, and invariant under the real involution. Applying the M\"obius transformation $f$ we can therefore say that $\iu v, z_0, \iu u$ all lie on a circle that is perpendicular to the imaginary axis and symmetric under reflection in the imaginary axis. Then $z_0$ lies on the circle
\[
x^2 + \bra{ y - \frac{u+v}{2} }^2 = \frac{(u-v)^2}{4},
\]
which simplifies to the relation
\[
x^2 + y^2 = y(u+v) - uv.
\]
These two circles intersect in two points: $z_0$ and $-\conj{z_0}$. The precise formulas are
\[
x = \frac{\sqrt{pw(u)w(v)}}{pw(v) + w(u)} \abs{u-v},\; y = \frac{puw(v) + vw(u)}{pw(v) + w(u)}
\]
where the sign of $x$ is chosen to make $z_0$ lie in the right half of the $z$-plane. This choice amounts to choosing the branch points $α,β$ inside the unit circle, as opposed to choicing their conjugate-inverse partners. Having found $z_0$ in terms of $(p,k,u,v)$ it remains to find the correct scaling of $f^{-1}$. We use the fact that $f^{-1}(\iu u) = 1$.
\begin{align*}
f^{-1}(z) &= C \frac{z-z_0}{z + \conj{z_0}} \\
1 = f^{-1}(\iu u) &= C \frac{\iu u - z_0}{\iu u + \conj{z_0}} \\
f^{-1}(z) &=  \frac{\iu u + \conj{z_0}}{\iu u - z_0} \frac{z-z_0}{z + \conj{z_0}}
\end{align*}
As was previously presented, one can simply take $α = f^{-1}(1)$ and $β = f^{-1}(k^{-1})$ to give formula for the branch points in terms of the new parameters.

In the case that one of $f(1)$ or $f(-1)$ is infinite, one needs to transistion to the coordinates $u'$ or $v'$ to maintain valid formulae. Though standard, it is perhaps still of some interest to consider the above geometrical argument in this limit. Suppose that $u' = 0$, which is to say geometrically that $1$ is mapped to infinity by $f$. Then the transformation $f$ takes the line through $1,0,-1$ to a line perpendicular to the imaginary axis, cutting at $f(-1)$. This line is therefore horizontal and so $z_0$ and $\iu v$ have the same imaginary parts. This gives $y=v$ directly. Considering next $p$, the special case of the cross ratio gives that
\begin{align}
p
&= \frac{\abs{z_0 -\iu v}^2}{\abs{1-\iu v}\abs{k^{-1}-\iu v}} \\
&= \frac{x^2}{k^{-1}\sqrt{1+v^2}\sqrt{1+k^2 v^2}} \\
x &= \sqrt{\frac{p w(\iu v)}{k}}.
\end{align}
These are the same formulas for $x$ and $y$ that one arrives by substituting $u = (u')^{-1}$ in the previous formulas and taking a limit $u' \to 0$. Given this modification of $z_0$, the rest of the formula for $f^{-1}$ is as before. The geometry for $f(-1) = \infty$ is similar. We summarise this in the following lemma.

\begin{lem}
The following maps between $\{ (α,β) \in D\times D | α \neq β \}$ and $P$ (def \ref{def:parameter space}) are diffeomorphisms. Recall $A, B$ (ref \todo{ref}), functions of $(α,β)$, and
\[
f(ζ) = \frac{ζ(\bar{α}A + B) - (A + αB)}{ζ(\bar{α}A - B) - (A - αB)}.
\]
Also recall from above $z_0$, a function of $(p,k,u,v)$ and
\[
f^{-1}(z) =  \frac{\iu u + \conj{z_0}}{\iu u - z_0} \frac{z-z_0}{z + \conj{z_0}}.
\]
The maps
\begin{align}
φ :     & \{ (α,β) \in D\times D | α \neq β \} \to P \\
        & (α,β) \mapsto (p(α,β), k(α,β), \Im f(1), \Im f(-1)),
\end{align}
and
\begin{align}
φ' :    & P \to \{ (α,β) \in D\times D | α \neq β \} \\
        & (p,k,u,v) \mapsto \left( f^{-1}(1), f^{-1}(k^{-1}) \right),
\end{align}
with the cases of $u'=0$ or $v'=0$ are dealt with with an appropriate limit, are well-defined mutually inverse diffeomorphisms.

\begin{proof}
These maps are inverses by construction above. We have not checked if the formulae are well-defined everywhere. For $φ'$ could potentially occur if $z_0$ were to equal $\iu u$, when the scaling factor would be $0/0$. This could only occur if $\Re{z_0}=0$, which itself only occurs if $u=v$. But this is exactly the plane which is excluded from $P$.

In the forward direction, $p$ and $k$ are well behaved functions. The only complicating situation is when $f(1)$ or $f(-1)$ is infinite, but this is exactly when $u'$ or $v'$ is zero. The functions could only fail to be smooth if they contain an expression of the form $\abs{g}$ at a point where $g=0$. Looking through the defintions of the formulae, this occurs when one of the following is the zero:
\[
u-v,\;\;    pw(u)w(v),\;\;      α-β,\;\;    1- \conj{α}β.
\]
The first is excluded from $P$, the second is never zero, the third is also excluded from the domain, and the last is zero, if and only if $\cji{α} - β =0$ which is impossible if both $α,β$ are inside the unit circle.
\end{proof}
\end{lem}



The moduli space $\mathcal{A}'_1$ is a subspace of this parameter space $P$ defined implicitly by the two conditions that $p$ and $T$ are constant. Having established formula for the inverse transformation from the new coordinates, it is time to rewrite $T_0$ in terms of $(p,k,u,v)$. Particularly, we must compute the factors in the third term of $T_0$. By direct computation
\begin{align*}
\abs{1-α} &= \abs{\frac{(z_0 + \conj{z_0}) (\iu u - 1) }{ (\iu u - z_0) (1 + z_0) }} \\
\abs{1-β} &= \abs{\frac{(z_0 + \conj{z_0}) (k \iu u - 1) }{ (\iu u - z_0) (1 + k z_0) }} \\
%%%%%%%%%%%%%%%%
\abs{α-β} &= \abs{\frac{\iu u + \conj{z_0}}{\iu u - z_0}} \abs{\frac{(z_0 + \conj{z_0}) (k - 1) }{ (1 + z_0) (1 + k z_0) }} \\
&= \abs{\frac{(z_0 + \conj{z_0}) (k - 1) }{ (1 + z_0) (1 + k z_0) }}
\\
%%%%%%%%%%%%%%%%
\abs{1-\conj{α}β} &= \abs{\frac{(z_0 + \conj{z_0}) (k + 1) }{ (1 + z_0) (1 + k z_0) }}.
\end{align*}
where the expressions were simplified using the observation that
\[
\abs{\frac{\iu u + \conj{z_0}}{\iu u - z_0}} = 1,
\]
because the denominator is the conjugate of the numerator. Next $ν = f^{-1}(\infty)$ and
so
\begin{align*}
ν &= \frac{\iu u + \conj{z_0}}{\iu u - z_0} \\
\frac{1+ν}{1-ν} &= -\iu \sqrt{\frac{w(u)}{pw(v)}}\sign{(u-v)} \\
\frac{1-ν}{1+ν} &= \iu \sqrt{\frac{pw(v)}{w(u)}}\sign{(u-v)} \\
\frac{4ν}{1-ν^2} &= \frac{1+ν}{1-ν} - \frac{1-ν}{1+ν} \\
&= -\iu \frac{pw(v) + w(u)}{\sqrt{pw(u)w(v)}} \sign{(u-v)}.
\end{align*}
These expressions combine to give
\begin{align*}
\frac{\abs{1-α}\abs{1-β}}{\abs{α-β} + \abs{1-\conj{α}β}} \frac{4ν}{1-ν^2}
&= \frac{1}{2}\abs{\frac{ (z_0 + \conj{z_0}) (1 - \iu u) (1-k\iu u) }{ (\iu u - z_0)^2 }}
    \times -\iu \frac{pw(v) + w(u)}{\sqrt{pw(u)w(v)}} \sign{(u-v)} \\
&= \frac{ \sqrt{pw(u)w(v)} }{ \abs{u - v}}
    \times -\iu \frac{pw(\iu v) + w(\iu u)}{\sqrt{pw(u)w(v)}} \sign{(u-v)} \\
&= -\iu \frac{ pw(\iu v) + w(\iu u) }{ u - v},
\end{align*}
and hence that
\begin{align*}
\labelthis{eqn:Teqn2}
2πT_0(p,k,u,v) = 4p \left[ E \tilde{F}(v) - K \tilde{E}(v) \right] - 4\left[ E \tilde{F}(u) - K \tilde{E}(u) \right] - 4K \frac{p w(v) + w(u)}{u-v}.
\end{align*}

We also need to express branch cuts of $T$ in the other coordinates of $P$, namely $u'$ and $v'$. First though, perhaps it is instructive to see how the locations of the branch cuts in terms of these new coordinates. $f(ν) = ∞$ and $f(1) = \iu u$, hence it follows that when $ν=1$ then $u' = 0$. And for the other marked point, $ν=-1$ when $v'=0$. So the branch cuts of $T_0$ on $P$ are precisely where $u$ and $v$ are not coordinates. Hence, in a sense, by giving branches of $T$ in each coordinate chart of $P$, we are giving a collection of functions on an open cover of $\mathcal{A}_1$ such that localy the function differ by constants.

To derive formulae that work on the other coordinate charts without re-expending the quantity of ink it has taken to get $T_0$, we draw on results from appendix REF \todo{ref} in which we establish how to extend some elliptic integrals analytically at infinity. In particular, let us consider the coordinate patch $(p,k,u,v')$. We rearrange the above to give
\[
2π T_0(p,k,u,v) = 4p \left[ E \left\{\tilde{F}(v)\right\} - K \left\{ \tilde{E}(v) - kv\right\} \right]
- 4 \left[ E \tilde{F}(u) - K \tilde{E}(u) \right]
- 4 K \left[\frac{p w(v) + w(u)}{u-v} - p k v \right] .
\]
Recall that $T$ on is defined up to the addition of mulitples of $1$ and $p$. By Legendre's formula,
\[
4π p = 4p\cdot 2\frac{π}{2}
= 4p \left[  2 E K' - 2 K (K' - E')  \right],
\]
so
\[
2π \left(T + 2p\right)
= 4p \left[ E \left\{2 K' + \tilde{F}(v)\right\} - K \left\{ 2(K'-E') + \tilde{E}(v) - kv\right\} \right]
- 4 \left[ E \tilde{F}(u) - K \tilde{E}(u) \right]
- 4 K \left[\frac{p w(v) + w(u)}{u-v} - p k v \right] .
\]
From lemma REF \todo{ref}, both
\[
\tilde{F} =
\begin{cases}
\tilde F((v')^{-1})             & \text{ for } v' > 0 \\
K'                              & \text{ for } v' = 0 \\
2\iu K' + \tilde F((v')^{-1}; k)   & \text{ for } v' < 0
\end{cases}
\]
and
\[
\tilde{E} - k(v')^{-1} :=
\begin{cases}
\tilde E((v')^{-1}) - k(x')^{-1}                 & \text{ for } v' > 0 \\
K'-E'                                            & \text{ for } v' = 0 \\
2(K'-E') + \tilde E((v')^{-1})  - k(v')^{-1}     & \text{ for } v' < 0
\end{cases}
\]
are analytic. These functions are precisely the forms seen in the braces in the above two expressions, and shows how we can write the first square bracket as a function of $v'$. The second square bracket is independent of $v$, so is trivially a function of $v'$. It remains to show
\[
\frac{p w(v) + w(u)}{u-v} - p k v
\]
is a smooth function of $v' \in \R$. Explicitly
\begin{align}
\frac{p w(v) + w(u)}{u-v} + p k v
&= \frac{pw(v) + w(u) + pkuv - pkv^2}{u-v} \\
&= p \frac{w(v) - kv^2}{u-v} + p \frac{kuv}{u-v} + \frac{w(u)}{u-v} \\
&= p \frac{1}{v'}\frac{\sqrt{(1+(v')^2)(k^2 + (v')^2)} - k }{uv'-1} + p \frac{ku}{uv'-1} + \frac{v' w(u)}{uv'-1},
\end{align}
which is analytic as the difference $\sqrt{(1+(v')^2)(k^2 + (v')^2)} - k$ vanishes quadratically in $v'$ near $v'=0$. The same trick in $u$ works if one wishes to write a formula for a branch cut of $T$ that is defined on $(p,k,u',v)$. Given these two tricks, it is automatic that one can apply both of them simultaneously to get a formula on $(p,k,u',v')$; the only point of concern would be the algebraic term in the simultaneous limit that $u',v' \to 0$, but the points where $u'=v'=0$ lie outside $P$. Thus, if we use the principal branch $T_0$ we can easily write formulae for other branches, even at $u'=0$ or $v'=0$, by the addition of constants and specifing the values at $u'=0$ or $v'=0$.



















\subsection{Covering the Parameter Space}

Consider the parameter space $P$ for a fixed value of $p$. Topologically it is the product of an interval cross and an annulus, a feature not easily seen from the $α,β$ description. The interval component is obvious, it comes from $k\in (0,1)$. To see the annulus part, consider $\RP^1 \times \RP^1$. Topologically $\RP^1$ is just a circle, so this product is a torus. The line $u=v$ can be represented as the line where the toroidal and poloidal angles are equal, and removing this line leaves an annulus.

A more instructive way of visualising $P$ is to think of it as a solid cylinder with a line along the central axis removed. One should think of the `radius' of point being given by $1-k$, so that the central axis is identified with the value $k=1$. To motivate this, consider the formula for $k$.
\[
k = \frac{\abs{1-\bar{α}β}-\abs{α-β}}{\abs{1-\bar{α}β}+\abs{α-β}}.
\]
In the limit as $α \to β$, this formula says that $k \to 1$. From the equation of $p$, for a fixed value of $p$, the subspace $α=β$ is an arc. In this visualisation we are imagining this arc as the central axis of the cylinder. In latter chapters, the interesting structure of the moduli space in this limit will be investigated.

Another way that this model is useful is it allows us to see the twisting in the space of spectral curve and the essential appearence of the period behaviour. Take a small loop around the central axis, which is to say a certain path in the space of spectral curves with $k$ close to $1$. This implies that $α$ and $β$ must be close together, and so the branch point circle is approximately a line.
As we move around the axis, the values of $f(1),f(-1)$ are moving through the values of $\RP^1$.
Another way to put this is that the points $μ,ν$ on the unit circle in the $ζ$-plane, which define the origin and infinity of the $z$-plane, are moving around the unit circle. Every time $ν$ crosses either $1$ or $-1$, we have moved across a branch cut, and an extra period term appears in our formulas.
We can infer from the rotation of $μ,ν$ that the branch point `line' is rotating about the point $(α, β)$, which in turn means that $α$ and $β$ are circling one another.
After one full rotation, $α$ and $β$ have returned to their original positions, but $T$ has been incremented by $1+p$. \todo{think about this}

Having derived local expressions, we shall now return our attention to $\tilde{T}$ defined on $\mathcal{P}$. We can naturally extend the coordinates of $P$ to $\mathcal{P}$ in the following way. Let the coordinates on $\mathcal{P}$ be
\[
\{(k,\tilde{u},\tilde{v}) \in (0,1)\times\R\times\R \mid  \tilde{v} -\tilde{u} \in 2π\Z  \}.
\]
The projection map $p : \tilde{P} \to P$ is given by
\begin{align*}
u &= \tan \frac{\tilde{u}}{2},
\quad  u' = \tan \frac{π - \tilde{u}}{2} = \cot \frac{\tilde{u}}{2}, \\
v &= \tan \frac{\tilde{v}}{2},
\quad  v' = \tan \frac{π - \tilde{v}}{2} = \cot \frac{\tilde{v}}{2}, \\
k &= k.
\end{align*}
To see why these coordinates parameterise the space of paths, it is instructive to consider how they can be used to give an expression for $\tilde{T}$. Define the winding number $W : \R \to \Z$ of a number $x$ to be the integer $W(x)$ such that $-π < x - 2πW(x) \leq π$. Then
\[
\tilde{T}(k,\tilde{u},\tilde{v}) = 2pW(\tilde{v}) - 2W(\tilde{u}) + T_0(k,u,v),
\]
where $\tilde{u},\tilde{v} \ni 2π\Z$. Recall an earlier comment about the fibre of the projection of $\mathcal{P}$ over $\mathcal{A}_1$: the paths between the marked points are in bijection with the signed number of crossings of a point. Take the point on the upper unit circle to be over $ν$. The assumptions on $\tilde{u},\tilde{v}$ imply that $ν$ will not be either $1$ or $-1$. The paths which do not cross this point are precisely the principal paths, hence $T_0$ in the formula. Other paths that differ by $n$ from the principal paths, differ in homology by $2n γ_I$. Thus the integrals of $Θ^2$ differ by $4π\iu n$. Putting this into the definition of $T$ gives the above.

The aptitude of $(k,\tilde{u},\tilde{v})$ to the job of parameterisation is in some sense the converse of this. Take some spectral curve such that $ν\neq\pm 1$. Then any path $γ_+$ can be described as a principal path plus some multiple $2n γ_I$. The principal paths themselves are described by $\iu u, \iu v$. We therefore assign $γ_+$ to be the number $\tilde{u} = u + 2π n$. And ditto for paths $γ_-$ vis-\`a-vis $\tilde{v}$. In the case that $ν$ is $1$ or $-1$, then we need to use the coordinates $u'$ or $v'$ and choose a different point to define the winding number with respect to, but the idea is the same. The restriction that $\tilde{u} -\tilde{v} \ni 2π\Z$ is exactly the condition that $u\neq v$.

We can now see that $\mathcal{P}$ is disconnected and how it is a cover of the universal cover of $\mathcal{A}_1$. $\mathcal{P}$ is $(0,1)\times\R^2$ with a family of parallel planes removed. Any connected region would serve as the universal cover of $\mathcal{A}_1$. One can characterise the components as follows. On any component, choose a point where $\tilde{u},\tilde{v} \in 2π\Z$. Then $W(\tilde{u}) - W(\tilde{v})$ is the same at all such points. Another way to think of this, is if you were trying to put paths $(γ_+,γ_-)$ into a more standard form, given any such pair over $Σ\in\mathcal{A}_1$ one moves through the space $\mathcal{P}$ to another point over $Σ$ such that $γ_+$ is principal. On exactly one component, $γ_-$ would be principal too, and one could order components of $\mathcal{P}$ by how many periods they fell short of this goal. As these components are essentially identical, we need only consider one of them. Let $\tilde{P}$ be the universal cover of $P$, identified with the specific component already mentioned, the one which has simultanously principal paths.
\[
\tilde{P} = \{(k,\tilde{u},\tilde{v}) \in (0,1)\times\R\times\R \mid  0 < \tilde{v} -\tilde{u} < 2π  \}.
\]

This all is entirely unsuprising. We already knew that $T$ was defined locally up to a constant, so of course $\tilde{T}$ can be locally described by a branch cut to $T$ and some constants. The useful part of this formula though is that it relates the abstractly defined $\tilde{T}$ to a set of coordinates that cover all of $\mathcal{P}$ (and therefore $\tilde{P}$) in a single chart and to a local expression $T_0$ that is written in coordinates expressly designed for ease of computation.





























\subsection{Derivaitves}

In the interest of having manageable formulae, we recall the definition of $w(y)^2 = (1+y^2)(1+k^2 y^2)$. Using primes to indicate coordinates at infinity (ie $y' = 1/y$), not derivatives, we introduce $w'(y')^2 = (1 + (y')^2)(k^2 + (y')^2)$. As $F(z;k)$ and $E(z;k)$ are parameter integrals in $z$, we have that
\[
\Partial{}{u} F(\iu u; k) = \frac{\iu}{w(u)},\;\;\;
\Partial{}{u} E(\iu u; k) = \iu\frac{1+k^2 u^2}{w(u)},
\]
and
\[
\Partial{}{u} w(u)
= \Partial{}{u} \sqrt{1+u^2}\sqrt{1+k^2 u^2}
= \frac{(1+k^2)u + 2k^2 u^3}{w(u)}.
\]
The other derivatives of elliptic integrals are calculated in appendix \ref{sec:Elliptic Integrals}. Equipped with these tools, the calculation of the derivatives of $T_0$ is elementary if tedious.
\begin{align*}\label{dTdk}
\frac{π}{2}\Partial{T_0}{k}
&= \frac{1}{k(1-k^2)}\frac{1}{u-v} \left[ p \sqrt { \frac{1+v^2}{1+k^2v^2}} + \sqrt { \frac{1+u^2}{1+k^2u^2} } \right] \left[ -(1+k^2uv) E + (1-k^2)K \right]
\end{align*}
\begin{equation}\label{dTdu}
\frac{π}{2}\Partial{T_0}{u}
= -\frac{E}{w(u)} + \frac{pK w(v)}{(u-v)^2} + \frac{K}{w(u)(u-v)^2}\left[1 + u^2 - uv + v^2 + k^2 uv + k^2 u^2v^2 \right]
\end{equation}
\begin{equation}\label{dTdv}
\frac{π}{2}\Partial{T_0}{v}
= \frac{pE}{w(v)} - \frac{K w(u)}{(u-v)^2} - \frac{pK}{w(v)(u-v)^2}\left[1 + u^2 - uv + v^2 + k^2 uv + k^2 u^2v^2 \right]
\end{equation}
While $T$ may be multivalued on $P$, its derivatives are not: the ambiguity of begin locally defined only up to a constant is removed by differentiation. Henceforth we can drop the subscript $0$ on derivatives.


\begin{equation}\label{dTdu'}
\frac{π}{2}\Partial{T_0}{u'}
= \frac{E}{w'(u')} + \frac{pK w(v)}{(1-u'v)^2} + \frac{K}{w'(u')(1-u'v)^2}\left[1 + k^2v^2 + - u'v + k^2u'v + (u')^2 + (u')^2v^2 \right]
\end{equation}
\begin{equation}\label{dTdv'}
\frac{π}{2}\Partial{T_0}{v'}
= -\frac{pE}{w'(v')} + \frac{K w(u)}{(uv'-1)^2} + \frac{pK}{w'(v')(uv'-1)^2}\left[1 + k^2u^2 - uv' + k^2uv' + (v')^2 + u^2(v')^2 \right]
\end{equation}

\begin{lem}
    \label{lem:deriv no zeroes}
The functions
\[
U(x,k,u,v) := -(u-v)^2 E + xKw(u)w(v) + K\left[ 1 + u^2 - uv + k^2 uv + v^2 + k^2 u^2 v^2 \right]
\]
and
\[
V(x,k,u,v') := -(uv'-1)^2 E + xKw(u)w'(v') + K\left[ 1 + k^2u^2 - uv' + k^2 uv' + (v')^2 + u^2 (v')^2 \right]
\]
have no zeroes for $x \geq 1$, $k\in (0,1)$, $u,v,v' \in \R$.
\begin{proof}
We shall prove this statement by showing that the two functions are in fact always positive. The first step is to eliminate $E$. From \cite{Anderson}, we have the sharp inequality $E < k^2 + (1-k^2)K$. If we apply the crude estimate that $K>1$ (in fact $K > π/2$), we see that
\[
E < k^2 + (1-k^2)K = K + k^2 (1-K) < K.
\]
Also using the assumption that $x\geq 1$, one can then begin
\begin{align*}
U(x,k,u,v)
&= -(u-v)^2 E + xKw(\iu u)w(\iu v) + K\left[ 1 + u^2 - uv + k^2 uv + v^2 + k^2 u^2 v^2 \right] \\
&> -(u-v)^2 K + Kw(\iu u)w(\iu v) + K\left[ 1 + u^2 - uv + k^2 uv + v^2 + k^2 u^2 v^2 \right] \\
&= K \left[ w(\iu u)w(\iu v) + 1 + (1 + k^2) uv + k^2 u^2 v^2 \right]
\end{align*}
This formula is almost sufficent. The only term that could be negative is the one featuring $uv$. However, a lower bound for the square root terms is
\[
w(u) = \sqrt{1 + (1+k^2)u^2 + k^2u^4} > \sqrt{(1+k^2)u^2} = \sqrt{(1+k^2)}\abs{u},
\]
so
\begin{align*}
U(x,k,u,v)
&> K \left[ (1+k^2)\abs{uv} + 1 + (1 + k^2) uv + k^2 u^2 v^2 \right] \\
&\geq K \left[ 1 + k^2 u^2 v^2 \right].
\end{align*}
This is positive, so $U$ is without zeroes. Taking a similar approach for $V$
\[
V(x,k,u,v') > K \left[ w(u) w'(v') + (1+k^2)uv' + k^2u^2 + (v')^2\right].
\]
In addition to the above bound for $w(u)$, we also now require a lower bound for $w'(v')$:
\[
w(v') = \sqrt{k^2 + (1+k^2)(v')^2 + (v')^4} > \sqrt{(1+k^2)(v')^2} = \sqrt{(1+k^2)}\abs{v'},
\]
which can now be applied to show that
\[
V(x,k,u,v') > K \left[k^2u^2 + (v')^2\right].
\]
This establishes that $V$ has no roots either.
\end{proof}
\end{lem}

This result is of interest because it shows that if $p \leq 1$, then the $v$ and $v'$ derivatives of $T$ are nonzero:
\begin{align*}
\frac{π}{2}\Partial{T}{v} &= \frac{-p}{w(v)(u-v)^2} U\bra{ \frac{1}{p},k,u,v }, \\
\frac{π}{2}\Partial{T}{v'} &= \frac{p}{w'(v')(uv'-1)^2} V\bra{ \frac{1}{p},k,u,v' }.
\end{align*}
And if $p \geq 1$, then the $u$ and $u'$ derivatives of $T$ are nonzero:
\begin{align*}
\frac{π}{2}\Partial{T}{u} &= \frac{1}{w(u)(u-v)^2} U\bra{ p,k,u,v }, \\
\frac{π}{2}\Partial{T}{u'} &= \frac{-1}{w'(u')(1-u'v)^2} V\bra{ p,k,v,u' }.
\end{align*}






\subsection{Topology of $\mathcal{M}$}
Recall that $\mathcal{M} \subset \mathcal{A}$ is the set of spectral curves that admit closing spectral data and that $\tilde{\mathcal{M}} \subset \tilde{P}$ is its preimage in the universal cover.

\begin{lem}
If $p \leq 1$ then $(k, \tilde{u})$ are coordinates on $\tilde{\mathcal{M}}$, and if $p \geq 1$ then $(k, \tilde{v})$ are coordinates on $\tilde{\mathcal{M}}$.

\begin{proof}
We prove this by direct application of the implict function theorem. Suppose first that $p \leq 1$. Consider the function $\tilde{T}(k,\tilde{u},\tilde{v})$ on $\tilde{P}$. Consider two formulae for its derivatives with respect to $\tilde{v}$.
\[
\Partial{\tilde{T}}{\tilde{v}}
= \Partial{T}{v}\frac{dv}{d\tilde{v}}
= \frac{1}{2}\sec^2\bfrac{\tilde{v}}{2} \Partial{T}{v},
\]
for $\tilde{v} \not\in π + 2π\Z$ and
\[
\Partial{\tilde{T}}{\tilde{v}}
= \Partial{T}{v'}\frac{dv'}{d\tilde{v}}
= -\frac{1}{2}\csc^2\bfrac{\tilde{v}}{2} \Partial{T}{v'},
\]
for $\tilde{v} \not\in 2π\Z$. As witnessed in Lemma \ref{lem:deriv no zeroes}, neither of the partial derivatives of $T$ with respect to $v$ or $v'$ are ever zero, and neither are $\sec$ or $\csc$. Hence $\partial \tilde{T} / \partial \tilde{v}$ is never zero. By the implicit function theorem therefore, there is a function $g$ such that the level set $\tilde{T}=q$ is a graph of the form $(k, \tilde{u}, g(k,\tilde{u}))$.

The same argument holds if $p \geq 1$, as then the $\tilde{u}$ derivative of $\tilde{T}$ is nonvanishing.
\end{proof}
\end{lem}

The topological implication of this is that each leaf of the moduli space $\tilde{\mathcal{M}}$ is diffeomorphic to a product of $(0,1)$ and $\R$ where $k$ is in the interval and the real parameter is either $\tilde{u}$ or $\tilde{v}$ depending on the magnitude of $p$. For brevity, we will refer to it as $x$. As the closing conditions are equivalent to $T$ begin rational, it follows that $\tilde{\mathcal{M}}$ for a fixed $p$ can be parameterised as $\Q\times(0,1)\times\R$. To understand the topology of $\mathcal{M}$, we must understand the action of the deck transformations as restricted to $\tilde{\mathcal{M}}$. The deck transformations $G$ are generated by the translation
\[
(k,\tilde{u},\tilde{v}) \mapsto (k, \tilde{u} + 2π, \tilde{v} + 2π).
\]
The corresponding effect on $\tilde{T}$ is
\[
\tilde{T}(k,\tilde{u} + 2π,\tilde{v} + 2π) \mapsto \tilde{T}(k, \tilde{u}, \tilde{v}) + 2(p-1).
\]
So in terms of the parameters $(q,k,x)$
\[
(q,k,x) \mapsto (q + 2(p-1), k, x + 2π).
\]
